Manuscript results: Forecasting influenza using ARIMA and ARIMAX

### 2025-07-28 manuscript_results.Rmd
update code

# Heatmap plot  
plot_m_heatmap <- ggplot(p_df, aes(x = factor(WeekAhead), y = Model, fill = m)) +
  geom_tile(aes(fill = ifelse(Significance == "Significant", m, NA)), color = "black") +  # Fill only significant ones
  geom_tile(data = p_df %>% filter(Significance == "Not Significant"), 
            aes(x = factor(WeekAhead), y = Model), fill = "gray80", color = "black") +  # Gray for non-significant
  geom_text(aes(label = paste0("m:", round(m, 1),", sd:", round(sd, 1))), 
            color = "black", size = 4) +  # Add text labels
  scale_fill_gradient2(
  low = "cyan", 
  mid = "white", 
  high = "red", 
  midpoint = 0,     # <-- Sets 0 as the midpoint
  na.value = "gray80", 
  name = "Mean difference", 
  limits = c(-35, 35)       
)+
  labs(title = "Mean differences between models' WIS and the baseline across 48 states",
       subtitle = "Gray boxes indicate models that are not significantly different from the baseline (p>0.05)",
         caption = "m = mean difference, sd = standard deviation",
       x = "Target Ahead",
       y = "") + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
  plot.caption = element_text(size = 16),
    plot.title = element_text(size = 18, face = "bold"),
    plot.subtitle = element_text(size = 14),) +
  facet_wrap(~ Model_Type, scales = "free_y")

@@

# Plot
effect_size<- ggplot(tidy_model_no_intercept, aes(x = term, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = estimate - std.error * 1.96,
                    ymax = estimate + std.error * 1.96),
                width = 0.2) +
  coord_flip() + 
  labs(
    title = "Effect size of model type, family and transformation on WIS difference",
    subtitle =  "WIS Difference relative to the AUTO type, ARIMA family and LogBack False (intercept)",
    y = "WIS Difference",
    x = ""
  ) +
  theme_minimal() + theme(plot.title = element_text(size = 16, face = "bold"),
                  plot.subtitle = element_text(size = 14))

>>>>

# Heatmap plot  
plot_m_heatmap <- ggplot(p_df, aes(x = factor(WeekAhead), y = Model, fill = m)) +
  geom_tile(aes(fill = ifelse(Significance == "Significant", m, NA)), color = "black") +  # Fill only significant ones
  geom_tile(data = p_df %>% filter(Significance == "Not Significant"), 
            aes(x = factor(WeekAhead), y = Model), fill = "gray80", color = "black") +  # Gray for non-significant
  geom_text(aes(label = paste0("m:", round(m, 1),", sd:", round(sd, 1))), 
            color = "black", size = 4) +  # Add text labels
  scale_fill_gradient2(
  low = "cyan", 
  mid = "white", 
  high = "red", 
  midpoint = 0,     # <-- Sets 0 as the midpoint
  na.value = "gray80", 
  name = "Mean difference", 
  limits = c(-35, 35)       
)+
  labs(title = "Mean differences between models' WIS and the baseline across 48 states",
       subtitle = "Gray boxes indicate models that are not significantly different from the baseline (p>0.05)",
         caption = "m = mean difference, sd = standard deviation",
       x = "Target Week",
       y = "") + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
  plot.caption = element_text(size = 16),
    plot.title = element_text(size = 18, face = "bold"),
    plot.subtitle = element_text(size = 14),) +
  facet_wrap(~ Model_Type, scales = "free_y")

@@

# Plot
effect_size<- ggplot(tidy_model_no_intercept, aes(x = term, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = estimate - std.error * 1.96,
                    ymax = estimate + std.error * 1.96),
                width = 0.2) +
  coord_flip() + 
  labs(
    title = "Effect size of model type, family and transformation on WIS difference",
    subtitle =  "WIS Difference relative to the AUTO type, ARIMA family and LogBack False (intercept)",
    y = "WIS Difference",
    x = "Model components"
  ) +
  theme_minimal() + theme(plot.title = element_text(size = 16, face = "bold"),
                  plot.subtitle = element_text(size = 14))
